---
title: "Statistical Inference - Project - 2 - ToolGrowth data analysis"
author: "Yannick Martel"
date: "17/09/2014"
output: pdf_document
---

1- Load the ToothGrowth data and perform some basic exploratory data analyses
----------------------------------------------------------

We perform loading, have quick look at data and plot a first graphical analysis.

```{r, results='asis'}
library(datasets)
library(ggplot2)
library(plyr)
library(knitr)

data(ToothGrowth)
kable(head(ToothGrowth, 4))
````

```{r}
str(ToothGrowth)
df=ToothGrowth
coplot(len ~ dose | supp, data = ToothGrowth, panel = panel.smooth,
       xlab = "ToothGrowth data: length vs dose, given type of supplement")
```


We find that:

- there seems to be a reaction to the Vitamin C on tooth growth, with higher response for a stronger dose;

- but the reaction seems to be different between delivery method: stronger reaction at lower dose for orange juice vs ascorbic acid.

2- Provide a basic summary of the data
----------------------------------------------------------

The population length response average is ```r mean(ToothGrowth$len)``` with standard error ```r sd(ToothGrowth$len)``` for a sample size of ```r length(ToothGrowth$len)```.

We can also compute length response means and standard errors per type of supplement and dose.

```{r, results="asis"}
s = ddply(ToothGrowth, .(supp, dose), summarise, 
          LenMean=mean(len), LenStdErr=sd(len), Count=length(len))
kable(s, format="markdown")
```

3- Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose
-------------------------------------------------------

From the analysis we have performed, we can set the following hypothesis:

- Ht: reponse to treatment is higher at low doses (0.5 and 1.0) when using orange juice (OJ) as compared to ascorbic acid (VC), but equivalent at higher dose (2.0).

We propose for this to test the hypothesis that:

- HaOJ and HaVC: growth is better at 2.0 dose than at 0.5 and 1.0, for OJ and VC, respectively

- Hb and Hc: growth is better with OJ than VC at 0.5 and 1.0 doses

- Hd: growth is equivalent with OJ and VC at 2.0

We test the hypothesis by calculating the 95% p-values with the ` t.test` R functino:

- HaOJ.1: len(dose 2.0, OJ) > len(dose 0.5, OJ), the p-value is 
`r t.test(df[df$supp=='OJ' & df$dose==2.0,]$len, df[df$supp=='OJ' & df$dose==0.5,]$len, paired=F, alternative='g')$p.value*100`%, 
which is lower than the 5% threshold, and thus we conclude than HaOJ.1 is valid.

- HaOJ.2: len(dose 2.0, OJ) > len(dose 1.0, OJ), the p-value is 
`r t.test(df[df$supp=='OJ' & df$dose==2.0,]$len, df[df$supp=='OJ' & df$dose==1.0,]$len, paired=F, alternative='g')$p.value*100`%, 
which is lower than the 5% threshold, and thus we conclude than HaOJ.2 is valid.

- HaVC.1: len(dose 2.0, VC) > len(dose 0.5, VC), the p-value is 
`r t.test(df[df$supp=='VC' & df$dose==2.0,]$len, df[df$supp=='VC' & df$dose==0.5,]$len, paired=F, alternative='g')$p.value*100`%, 
which is lower than the 5% threshold, and thus we conclude than HaVC.1 is valid.

- HaVC.2: len(dose 2.0, VC) > len(dose 1.0, VC), the p-value is 
`r t.test(df[df$supp=='VC' & df$dose==2.0,]$len, df[df$supp=='VC' & df$dose==1.0,]$len, paired=F, alternative='g')$p.value*100`%, 
which is lower than the 5% threshold, and thus we conclude than HaVC.2 is valid.

- Hb: len(dose 0.5, OJ) > len(dose 0.5, VC), the p-value is 
`r t.test(df[df$supp=='OJ' & df$dose==0.5,]$len, df[df$supp=='VC' & df$dose==0.5,]$len, paired=F, alternative='g')$p.value*100`%, 
which is lower than the 5% threshold, and thus we conclude than Hb is valid.

- Hc: len(dose 1, OJ) > len(dose 1, VC), the p-value is 
`r t.test(df[df$supp=='OJ' & df$dose==1,]$len, df[df$supp=='VC' & df$dose==1,]$len, paired=F, alternative='g')$p.value*100`%, 
which is lower than the 5% threshold, and thus we conclude than Hc is valid.

The comparison between the 2.0 doses of OJ and VC is more complex:

- if we take len(dose 2.0, OJ) == len(dose 2.0, VC) as null hypothesis, we get a two-sided p-value of 
`r t.test(df[df$supp=='OJ' & df$dose==2.0,]$len, df[df$supp=='VC' & df$dose==2.0,]$len, paired=F, alternative='two.sided')$p.value*100`%.
Thus we cannot disregard the null hypothesis.

- on the other hand we can take first as H0 hypothesis len(dose 2.0, OJ) == len(dose 2.0, VC) + 3.5, and as H1 hypothesis that len(dose 2.0, OJ) < len(dose 2.0, VC) + 4. We compute the p-value of H1 as 
`r t.test(df[df$supp=='OJ' & df$dose==2.0,]$len, df[df$supp=='VC' & df$dose==2.0,]$len+4, paired=F, alternative='l')$p.value * 100`%, 
which is lower than 2.5%, and thus we conclude that H1 is valid with 97.5% confidence.

- then we take as H0 len(dose 2.0, OJ) == len(dose 2.0, VC) - 4, and as H1 hypothesis that len(dose 2.0, OJ) > len(dose 2.0, VC) - 3.5. We compute the p-value of H1 as 
`r t.test(df[df$supp=='OJ' & df$dose==2.0,]$len, df[df$supp=='VC' & df$dose==2.0,]$len-4, paired=F, alternative='g')$p.value * 100`%, which is lower than 2.5%, and thus we conclude that H1 is valid with 97.5% confidence.

Thus we prove that len(dose 2.0, OJ) and len(dose 2.0, VC) are close together in a [-4, 4] interval with 95% confidence.

4. State your conclusions and the assumptions needed for your conclusions
--------------------------------------------------------------------------------------------

From what we have found, we can safely conclude that:

- with all delivery methods, teeth growth improves from 0.5 mg dose to 2.0 mg dose, and from 1.0 mg to 2.0 mg;

- with 0.5 mg and 1.0 mg doses, teeth growth improves more with orange juice delivery method than ascorbic acid;

- with a 2.0 mg dose, we cannot show that there is a difference in result between the two delivery methods. On the contrary, the results seem to be close together within a [-4, 4] interval.








