---
title: "Statistical Inference - Project - 1 - Simulation exercise"
author: "Yannick Martel"
date: "17/09/2014"
output: pdf_document
---

1- Load the ToothGrowth data and perform some basic exploratory data analyses
----------------------------------------------------------

We perform loading, have quick look at data and plot a first graphical analysis.

```{r}
library(datasets)
library(ggplot2)
library(plyr)
library(knitr)

head(ToothGrowth)
data(ToothGrowth)
coplot(len ~ dose | supp, data = ToothGrowth, panel = panel.smooth,
       xlab = "ToothGrowth data: length vs dose, given type of supplement")
```

We find that:
- there seems to be a reaction to the Vitamin C on tooth growth, with higher response for a stronger dose;
- but the reaction seems to be different between delivery method: stronger reaction at lower dose for orange juice vs ascorbic acid.

2- Provide a basic summary of the data
----------------------------------------------------------

The population length response average is ```r mean(ToothGrowth$len)``` with standard error ```r sd(ToothGrowth$len)``` for a sample size of ```r length(ToothGrowth$len)```.

We can also compute length response means and standard errors per type of supplement and dose.

```{r, results="asis"}
s = ddply(ToothGrowth, .(supp, dose), summarise, 
          LenMean=mean(len), LenStdErr=sd(len), Count=length(len))
kable(s, format="markdown")
```

3- Use confidence intervals and hypothesis tests to compare tooth growth by supp and dose
-------------------------------------------------------

From the analysis we have performed, we can set the following hypothesis:
- Ht: reponse to treatment is better at low doses (0.5 and 1.0) when using orange juice (OJ) as compared to ascorbic acid (VC), but equivalent at higher dose (2.0).

We propose for this to test the hypothesis that:

- HaOJ and HaVC: growth is better at 2.0 dose than at 5.0 for OJ and VC, respectively

- Hb and Hc: growth is better with OJ than VC at 0.5 and 1.0 doses

- Hd: growth is equivalent with OJ and VC at 2.0 (and thus the null hypothesis is that the length respose are different between the two delivery methods)

We define the following function for calculating the confidence interval for the difference of two sub-populations:

```{r}
tConfidence = function (X, Y, p) {
        df = (X$LenStdErr^2 / X$Count + Y$LenStdErr^2 / Y$Count) /
                ((X$LenStdErr^2/X$Count)^2 / (X$Count-1) + 
                         (Y$LenStdErr^2/Y$Count)^2 / (Y$Count-1))
        Y$LenMean - X$LenMean + 
                c(-1,1) * qt(p, df) * sqrt(X$LenStdErr^2/X$Count + Y$LenStdErr^2/Y$Count)
}
```

To test this hypothesis, we calculate 95% T-confidence intervals:

- HaOJ: len(dose 2.0, OJ) > len(dose 0.5, OJ), confidence interval for difference is ```r tConfidence(s[1,], s[3,], 0.95)```. As the interval is all over 0, we can conclude than HaOJ is valid.

- HaVC: len(dose 2.0, VC) > len(dose 0.5, VC), confidence interval for difference is ```r tConfidence(s[4,], s[6,], 0.95)```. As the interval is all over 0, we can conclude than HaVC is valid.

- Hb: len(dose 0.5, OJ) > len(dose 0.5, VC), confidence interval for difference is ```r tConfidence(s[4,], s[1,], 0.95)```. As the interval is all over 0, we can conclude that Hb is valid.

- Hc: len(dose 1.0, OJ) > len(dose 1.0, VC), confidence interval for difference is ```r tConfidence(s[5,], s[2,], 0.95)```. As the interval is all over 0, we can conclude that Hc is valid.

- Hd: len(dose 2.0, OJ) == len(dose 2.0, VC), confidence interval for difference is ```r tConfidence(s[6,], s[3,], 0.55)```. 

